# Demo for Rmarkdown

## Description
We are using data from [Ben Aissa et al (2019) ](https://pubmed.ncbi.nlm.nih.gov/31668811-aahiv-a-sodium-channel-scorpion-toxin-inhibits-the-proliferation-of-du145-prostate-cancer-cells/?from_term=houcemeddine+othman&from_sort=date&from_pos=1) to test the significativity of 15ng/microliter of a peptide relative to controle on DU145 prostate cancer cell line adhesion. 

## statistical significance
$H_0$: there is no difference of cell migration between the controle samples and  the sample treated with the peptide. 

$H_A$: There is a difference. 

$\alpha=0.05$

```{r }
library(tidyverse)
setwd("../data/")
adhesion <- read.csv("adhesion_aah4.csv")
Cn<-filter( adhesion, Sample=="Controle" )
adhesion$inhibition <- (adhesion$OD/mean(Cn$OD))*100


aah4 <- filter(adhesion, adhesion$Sample == "AaHIV")
controle <- filter(adhesion, adhesion$Sample != "AaHIV")
t.test(aah4$inhibition, controle$inhibition, alternative="t")

```

## Plotting the activity 

```{r adhesion }
library(ggpubr)
ggbarplot(adhesion, x = "Sample", y = "inhibition", add = c("mean_se")
          ,color = "Sample", fill = "Sample",alpha=0.3, palette = "Dark2", width = 0.4, ylab="inhibition %", xlab=FALSE )+ theme(legend.position="none", text = element_text(size=15))
          
```
